---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# plotrix

<!-- badges: start -->
<!-- badges: end -->

`plotrix` is an `R` package that provides many plotting, labeling, and axis &
color scaling functions.  


## Installation

You can install the current release of `plotrix` from CRAN with:

``` r
install.packages("plotrix")
```

You can install the development version of plotrix from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("dmurdoch/plotrix")
```

## Authors


The original author and maintainer of `plotrix`, Jim Lemon, passed away in
September 2023. 

Currently it is being maintained by Duncan Murdoch.  Please submit
bug reports to https://github.com/dmurdoch/plotrix/issues.  

```{r echo = FALSE}
authors <- eval(parse(text = packageDescription("plotrix")$Authors))

keep <- sapply(authors, function(a) !any((c("aut", "cre") %in% a$role)))
```

Other contributors include:

`r paste(authors[keep], collapse=",  \n")`.


